---
title: "Analysis by County"
author: ""
date: "4/27/2018"
output: html_document:
    code_folding: hide
---

```{r}
library(fivethirtyeight)
library(tidyverse)
library(dplyr)
library(mosaic)
View(police_killings)
```


# Analysis by County
Kendra and Yifan, something like this! Where every row is a county. Use this data for your analysis. 

Maybe add some more vairbales now that you see how it works. 

```{r}
county_data <- police_killings %>%
  mutate(g = ifelse(gender == "Male", 1, 0),
         w = ifelse(raceethnicity == "White", 1,0)) %>%
  group_by(county_id) %>%
  summarise(n_deaths = n(),
            tot_pop = sum(pop, na.rm=TRUE), 
            n_male = sum(g),
            n_white = sum(w, na.rm=TRUE),
            avg_pov = mean(pov, na.rm=TRUE),
            avg_urate = mean(urate, na.rm=TRUE),
            avg_college = mean(college, na.rm=TRUE)) %>%
  mutate(percent_m = n_male/n_deaths, 
         prop_n_deaths = n_deaths/tot_pop*1000,
         percent_white = n_white/n_deaths)
county_data
```

```{r}
ggplot(county_data, aes(x = prop_n_deaths)) +
  geom_histogram()
```

Then you can fit some linear models, like this

```{r}
a_model_for_you <- lm(prop_n_deaths ~ n_male + n_white + avg_pov + avg_urate + avg_college, data = county_data)

summary(a_model_for_you)
```

diagnostics

```{r}
plot(a_model_for_you)
```

Make some bivariate scatterplots here. 

```{r}

```



```{r}
# z <- police_killings %>%
#   group_by(county_id) %>%
#   summarise(nod = n()) 
# 
# a <- police_killings %>%
#   select(county_income, county_id) %>%
#   right_join(z, by = "county_id")
# 
# c <- police_killings %>%
#   select(raceethnicity, county_id)%>%
#   filter(!is.na(raceethnicity)) %>%
#   mutate(w = ifelse(raceethnicity == "White", 1,0))%>%
#   group_by(county_id) %>%
#   summarise(n_w = sum(w))
```

```{r}
# base <- police_killings %>%
#   select(county_id, gender) %>%
#   mutate(g = ifelse(gender == "Male", 1, 0)) %>%
#   group_by(county_id)%>%
#   summarise(n_g = sum(g)) %>%
#   right_join(a, by = "county_id") %>%
#   mutate(percent_m = n_g/nod) %>%
#   right_join(c, by = "county_id") %>%
#   mutate(percent_w = n_w/nod)

