---
title: "Analysis by County"
author: "Kendra Swanson, Yifan Ma"
date: "4/27/2018"
output: html_document
---

```{r, include = FALSE}
library(fivethirtyeight)
library(tidyverse)
library(dplyr)
library(mosaic)
library(ggplot2)
data(police_killings)
```

```{r}
county_data <- police_killings %>%
  mutate(g = ifelse(gender == "Male", 1, 0),
         w = ifelse(raceethnicity == "White", 1,0)) %>%
  group_by(county_id) %>%
  summarise(n_deaths = n(),
            tot_pop = sum(pop, na.rm=TRUE), 
            n_male = sum(g),
            n_white = sum(w, na.rm=TRUE),
            avg_pov = mean(pov, na.rm=TRUE),
            avg_urate = mean(urate, na.rm=TRUE),
            avg_college = mean(college, na.rm=TRUE)) %>%
  mutate(percent_m = n_male/n_deaths, 
         prop_n_deaths = n_deaths/tot_pop*1000,
         percent_white = n_white/n_deaths)
head(county_data, 10)
```

```{r}
a_model_for_you <- lm(prop_n_deaths ~ percent_m + percent_white + avg_pov + avg_urate + avg_college, data = county_data)

summary(a_model_for_you)
```

```{r}
a_model_for_you2 <- lm(prop_n_deaths ~avg_pov + avg_urate, data = county_data)

summary(a_model_for_you2)
```

```{r}
a_model_for_you3 <- lm(prop_n_deaths ~ percent_m + percent_white + avg_urate + avg_college, data = county_data)

summary(a_model_for_you3)
```

```{r}
a_model_for_you4 <- lm(prop_n_deaths ~ percent_m + percent_white + avg_pov+ avg_college, data = county_data)

summary(a_model_for_you4)
```


### Diagnostics

```{r}
plot(a_model_for_you)
```

### Bivariate scatterplots


```{r}
ggplot(county_data, aes(x = n_white, y = prop_n_deaths))+
         geom_point(stat = "identity")
```

### Which county are the outliers

```{r}
outliers <- county_data %>%
  left_join(police_killings, by = "county_id") %>%
  select(county_id:percent_white, city, state)%>%
  mutate (o = percent_white/prop_n_deaths) %>%
  arrange (desc(o))%>%
  head(10)
```


### Comparison of race distribution of victims 

```{r}
county_data <- county_data %>%
  mutate(majority_white_deaths = ifelse(percent_white >= 0.5, 1, 0))
```

```{r}
ggplot(data = county_data, aes(x = majority_white_deaths, y = prop_n_deaths)) + geom_boxplot(aes(group = majority_white_deaths))
```
 
This graph shows the deaths per 1000 people for counties in which greater than or equal to 50% of the people killed were white, compared to counties in which greater than 50% of the people killed were not. We counted counties in which white and nonwhite people were killed in equal amounts as majority_white_deaths = true.

# Find confidence interval for difference in means

```{r}
t.test(prop_n_deaths ~ majority_white_deaths, data = county_data)
```

We are 95% confident that in counties where the majority of police killings happened to non-white individuals, the mean deaths per thousand residents of those counties is between 1.6%  and 9.2% higher than the mean deaths per thousand in counties where the majority of police killings happened to white individuals.


```{r}
ggplot(county_data, aes(x = avg_pov, y = prop_n_deaths, color = avg_urate))+
         geom_point()+
         geom_lm()

mod_p <- lm(prop_n_deaths~avg_pov, data = county_data)
summary(mod_p)
confint(mod_p)
```

We found that for every one percent increase in average poverty rate in the county, we would predict a 4 percent increase in death per thousand people in that county, holding all other variable constant.

We are 95% confident that the true slope value of death per thousand and poverty rate is between .003 and .006. 

```{r}
outliers2 <- county_data %>%
  left_join(police_killings, by = "county_id") %>%
  select(avg_pov, tot_pop, avg_urate, city, state)%>%
  arrange (desc(avg_pov))%>%
  head(5)

outliers3 <- county_data %>%
  left_join(police_killings, by = "county_id") %>%
  select(prop_n_deaths, avg_pov, tot_pop, avg_urate, city, state)%>%
  arrange (desc(prop_n_deaths))%>%
  head(5)
outliers2
outliers3
```

Highest poverty rate: a county in Charlotte NC.
Highest death per thousand: a county in Fort Pierce, FL, with average poverty rate of 54.2. Fort Pierce have 30.2% of the population below the poverty line as a city.

```{r}
ggplot(county_data, aes(x =  avg_urate, y = prop_n_deaths))+
         geom_point()+
         geom_lm()

mod_u <- lm(prop_n_deaths~avg_urate, data = county_data)
summary(mod_u)
confint(mod_u)
```

We found that every one percent increase in unemployment rate in the county, we would predict a 72 percent increase in death per thousand people in that county, holding all other variable constant.

We are 95% confident that the true slope value of death per thousand and unemployment rate is between .46 and .97. 

```{r}
mod_pu <- lm(avg_pov~avg_urate, data = county_data)
summary(mod_pu)
confint(mod_pu)
```

Average umployment rate is postively correlated to average poverty rate. The result is also signifant, p < 0.05. 
