---
title: "Technical report"
author: "Yifan Ma & Kendra Swanson"
date: "April 23, 2018"
output: 
  html_document:
    code_folding: hide
    df_print: paged 
---

```{r}
library(fivethirtyeight)
library(tidyverse)
library(dplyr)
library(mosaic)
library(maps)
library(mapdata)
View(police_killings)
police_killings_2015 <- read.csv("the-counted-2015.csv")
```

```{r}
c <- police_killings %>%
  group_by(state) %>%
  summarise(sum = n())%>%
  arrange(desc(sum))
# need divide by population 


library(readxl)
state_a <- read_excel("state_a.xls")
states <- map_data("state")
states <- states %>%
  left_join(state_a, by = c("region" = "State")) %>%
  full_join(c, by = c("Abreviation" = "state"))

base <- ggplot(data = states) + 
  geom_polygon(aes(x = long, y = lat, group = group, fill = sum), color = "white")+
  scale_fill_gradient(low = "grey", high = "red")+
  theme(legend.position="right")+
  theme_void()+
  coord_fixed(1.3)

base
```


```{r}
a <- police_killings %>%
  group_by(armed, state) %>%
  summarise(s = n()) %>%
  arrange(desc(s)) 

```

```{r}
g <- police_killings %>%
  group_by(gender, state) %>%
  summarise(s = n()) %>%
  arrange(desc(s)) 
```

```{r}
a_s1 <- police_killings %>%
  group_by(age) %>%
  summarise(s = n()) %>%
  arrange(desc(s)) 

ggplot(a_s1, aes(x = age, y = s)) +
  geom_line()
  

a_s2 <- police_killings %>%
  group_by(age, state) %>%
  summarise(s = n()) %>%
  arrange(desc(s)) 

```


```{r}
mod <- lm( ~county_income + age + gender + armed + raceethnicity )
```

```{r}

```







### Distribution of county income for 

```{r}
police_killings %>%
  ggplot(aes(x = county_income)) + geom_histogram(bins = 30)
```

```{r}
favstats(~county_income, data = police_killings)
```

Median income for the county in which police killings occurred in 2015 was $50,877, while median household income in 2015 for all of the USA was $56,516. (source: https://www.census.gov/library/publications/2016/demo/p60-256.html)

- Is this statistically significant?
- comp_income = the ratio of the median household income in the tract (specific neighborhood?) in which the killing happened, to the median household income of the county as a whole --> examine this?

```{r}

```



